The dynamic stiffness matrix based on the extended separation-of-variables type solution for the free vibration of orthotropic rectangular thin plates

### 2025-05-13 Paper7.tex
SM revise

% I made some comments about x/L being xi - it's not used much so you can ignore these.
% There are some cases where I added text in [square brackets] and not necessarily in a latex comment
% Check the bib file - two references had no journal - I added these as XXXX
% Section 4 does too much - could you consider splitting this section up a bit? 
% I did add some more subsubsections to try structure section 4 a bit better, but I'm not sure it's optimal yet.
\begin{frontmatter}
\title{The dynamic stiffness matrix based on the extended separation-of-variables type solutions for the free vibration of orthotropic rectangular thin plates}
\author[1]{Shiyi Mei}\ead{shiyi.mei1@monash.edu}
\author[1]{Colin Caprani\corref{cor1}}\ead{colin.caprani@monash.edu}
\author[2]{Daniel Cantero}\ead{daniel.cantero@ntnu.no}
\cortext[cor1]{Corresponding author}
\affiliation[1]{organization={Department of Civil Engineering, Monash University},city={Melbourne},state={Victoria},country={Australia}}
\affiliation[2]{organization={Department of Structural Engineering, Norwegian University of Science \& Technology NTNU},city={Trondheim}, country={Norway}}
\begin{abstract}
The dynamic stiffness matrix based on the extended separation-of-variables mode functions is developed for the free vibration analysis of an orthotropic rectangular thin plate with general homogeneous boundary conditions.  
The governing differential equation and boundary conditions are derived from Rayleigh’s principle.  
Based on the boundary conditions, the dynamic stiffness matrix is formulated and solved using an improved Wittrick-Williams algorithm.  
In this improved algorithm, simply supported frequencies are required instead of fully clamped frequencies, and the closed-form expression for the simply supported frequencies is provided, enhancing the efficiency and systematicity of solving the eigenvalue problem.  
The proposed method is validated by the numerical experiments.
\end{abstract}
\end{frontmatter}
\linenumbers
\section{Introduction}
Rectangular plates play an important role in various engineering fields, including civil, mechanical, and aerospace engineering \citep{biancolini2005approximate}. 
The free vibration of plates has been a fundamental research problem for over two centuries. 
The earliest exact solutions for this problem are the Navier \citep{navier1823extrait} and Levy \citep{levy1899equilibre} solutions, which require at least one pair of opposite edges to be simply supported or guided.
To solve problems with other boundary conditions, approximate solutions such as the Rayleigh–Ritz method \cite{leissa1973free} and the Galerkin method \cite{laura1967study} have been widely applied. 
For these approximation methods, beam functions, polynomials, trigonometric functions, and their combinations \cite{li2004vibration} are commonly used as the assumed approximate functions.
The accuracy of these solutions depends on how well the assumed approximate functions represent the displacement of the plate.

@@

Despite being a powerful method for the dynamic analysis of plate assemblies, the finite element method (FEM) requires a sufficient number of elements and is computationally expensive to accurately capture higher-order modes.
Thus, the DSM method is developed as an accurate and efficient analytical approach to alternatively solve complex plate structures \cite{boscolo2011dynamic,fazzolari2013exact}. 
The DSM can be considered as an analytical FEM since the mode functions of the plate are expressed by analytical solutions, where Levy-type solution \cite{ghorbel2015dynamic} or components of infinite Fourier series \cite{banerjee2015dynamic,liu2016free} are applied.
To avoid solving the cumbersome transcendental frequency equation directly, the Wittrick-Williams (W-W) algorithm \cite{wittrick1971general} is applied to the eigenvalue problem.
The W-W algorithm determines the lower and upper bounds of natural frequencies rather than solving the frequency equation directly. 
Thus, the DSM has the potential to be effectively and systematically solved using the W-W algorithm.
However, a critical part in applying the W-W algorithm is to priorly determine all natural frequencies of the fully clamped structure within the interested frequency range.
Strategies such as using a sufficiently fine mesh or including a sufficient number of terms in series expansions \cite{banerjee2015dynamic} can ensure that all fully clamped frequencies are accounted for, thereby maintaining the accuracy of the algorithm. However, these approaches are computationally expensive and complex, posing a significant obstacle to the wider adoption and application of the DSM method based on the W-W algorithm \cite{han2018improved}.
To resolve the fully clamped plate problem, \citet{liu2015exact} suggested that the fully clamped frequencies can be indirectly obtained from the simply supported plate problem, where the Navier solution serves as the analytical solution. This provides a significant enhancement to the W-W algorithm, increasing the efficiency of applying DSM methods. 
However, since infinite-term series expansion-based solutions are used for plate analysis instead of explicit and closed-form solutions, a sufficient number of truncation terms is required to ensure accuracy and capture the necessary modal degrees.

Inspired by the Navier and Levy solutions, \citet{xing2009new} proposed the separation-of-variables (SOV) method, which provides concise and explicit eigensolutions.
The mode shape function has a separable form, $\phi(x) \psi(y)$, requiring only one $\phi(x)$ and one $\psi(y)$ for each mode order, allowing each eigenvalue equation to be explicitly expressed.
However, this SOV method is not suitable to deal with plate with free boundary conditions.
Therefore, an extended SOV method \cite{xing2018overall, xing2020extended} based on the Rayleigh quotient is proposed to accommodate plates with all classical boundary conditions, i.e., simply supported, clamped, guided, and free.
Based on the Rayleigh quotient model, alternative iterative and improved SOV methods have been subsequently proposed \cite{xing2020improved}.
Although SOV methods provide concise closed-form analytical solutions, solving the highly nonlinear eigenvalue equations is required.

In this study, the free vibration of orthotropic plates with general boundary conditions is analyzed by extending the SOV method based on the Rayleigh quotient to obtain the solution for elastically restrained plates.
Subsequently, dynamic stiffness matrices in both the \(x\) and \(y\) directions, derived from the SOV-form solutions, are developed to solve the eigenvalue problem.
By applying the 'hypothetical structure method', a modified W-W algorithm is developed, requiring only the natural frequencies of the simply supported structure instead of the necessity of fully clamped frequencies.
The concise closed-form expression for the simply supported frequencies is directly obtained from the eigenvalue equation based on the SOV method, eliminating the extensive computational effort typically required in DSM methods to determine all fully clamped frequencies within the frequency range.  
Therefore, this approach can improve the systematic and effective application of the DSM method depending on the W-W algorithm.
Alternatively, it can also be considered as an efficient technique for solving transcendental eigenvalue equations in the SOV method.

@@

The governing differential equation for the free vibration of a thin orthotropic plate is given by \citep{xing2020improved}:  
%
\begin{equation}\label{eq:governing_EOM}
	D_{11}\frac{\partial^4w}{\partial \xi^4} + 2D_3\alpha^2\frac{\partial^4w}{\partial \xi^2 \partial \eta^2} + D_{22}\alpha^4\frac{\partial^4w}{\partial \eta^4} = \rho h\alpha^4\omega^2w,
\end{equation}
%
where the bending stiffness parameters are defined as:
%
\begin{equation}\label{eq:bd_stiff}
	\begin{split}
		&D_{11} = \frac{E_1h^3}{12(1-v_{12}v_{21})}, \quad D_{22} = \frac{E_2h^3}{12(1-v_{12}v_{21})}, \\  
		&D_{66} = \frac{G_{12}h^3}{12}, \quad D_{12} = v_{12}D_{22} = v_{21}D_{11}, \quad D_3 = D_{12} + 2D_{66},
	\end{split}
\end{equation}
%
where \(\rho\) and \(h\) denote the mass density and thickness of the plate, respectively; \(E_1\) and \(E_2\) are the Young’s moduli in the \(x\)- and \(y\)-directions, respectively; \(G_{12}\) is the shear modulus, and \(v_{12}\) and \(v_{21}\) are the Poisson’s ratios.

@@

Assuming the solution of the deflection \( W(x, y; t) = w(x, y) e^{i \omega t} \) for harmonic plate motion, 
where \( \ii = \sqrt{-1} \), \( w(x, y) \) is the mode shape, and \( \omega \) is the radial frequency.  
By substituting \( W(x, y; t) = w(x, y) e^{i \omega t} \) into \Cref{eq:poten_energy,eq:kine_energy} and expressing the system in dimensionless coordinates, we have:
%
\begin{equation}\label{eq:poten_energy_mag}
	\begin{split}
		U_{\text{mag}}^{I} &= \frac{ab}{2} \iint \left[ \frac{D_{11}}{a^4} \left( \frac{\partial^2 w}{\partial \xi^2} \right)^2 + \frac{2 D_{12}}{a^2 b^2} \frac{\partial^2 w}{\partial \xi^2} \frac{\partial^2 w}{\partial \eta^2} + \frac{D_{22}}{b^4} \left( \frac{\partial^2 w}{\partial \eta^2} \right)^2 \right. \\
		&\quad \left. + \frac{4 D_{66}}{a^2 b^2} \left( \frac{\partial^2 w}{\partial \xi \partial \eta} \right)^2 \right] \, \mathrm{d} \xi \, \mathrm{d} \eta,
	\end{split}
\end{equation}
%
and
%
\begin{equation}\label{eq:kine_energy_mag}
	\begin{split}
		T &= \omega^2 \frac{ab}{2} \rho h \iint w^2 \, \mathrm{d} \xi \, \mathrm{d} \eta = \omega^2 T_0
	\end{split},
\end{equation}
%
where \( \alpha = a / b \) is the aspect ratio; \( \xi = x / a \) and \( \eta = y / b \) are the normalized coordinates.
The separable form of the mode shape function \( w(\xi, \eta) \) is given by:
%
\begin{equation}\label{eq:displace_func}
	w(\xi, \eta) = \phi(\xi) \psi(\eta),
\end{equation}
%
where \( \phi(\xi) \) and \( \psi(\eta) \) can be expressed as:
\begin{subequations}\label{eq:phi_psi_solution}
	\begin{align}
		\phi(\xi) &= A_1 \sin{(\alpha_1 \xi)} + A_2 \cos{(\alpha_1 \xi)} + A_3 \sinh{(\beta_1 \xi)} + A_4 \cosh{(\beta_1 \xi)},\label{eq:phi_solution1}\\
		\psi(\eta) &= B_1 \sin{(\alpha_2 \eta)} + B_2 \cos{(\alpha_2 \eta)} + B_3 \sinh{(\beta_2 \eta)} + B_4 \cosh{(\beta_2 \eta)}. \label{eq:phi_solution2}
	\end{align}
\end{subequations}

It should be noted that \Cref{eq:governing_EOM} represents the strong-form governing equation of the orthotropic plate, while \Cref{eq:Rayleigh} is the weak-form governing equation, with the latter being equivalent to the former.
Based on \Cref{eq:Rayleigh}, the frequencies $\omega_x$ and $\omega_y$, corresponding to the mode shapes $\phi(\xi)$ and $\psi(\eta)$, respectively, are assumed to be independent of each other.

@@

For given general homogeneous boundary conditions, we can first assume that the mode shape $\psi(\eta)$ corresponding to the $y$ direction is known. 

@@

		&=\frac{ab}{2} \int_{-1}^{1} \left[ \frac{D_{11}}{a^4}S_1 \left( \frac{\id^2\phi }{\id \xi^2} \right)^2 + \frac{2 D_{12}}{a^2 b^2}S_2 \frac{\id^2\phi }{\id \xi^2}\phi  + \frac{D_{22}}{b^4}S_4  \phi^2 \right. \\
		&\quad \left. + \frac{4 D_{66}}{a^2 b^2}S_3 \left( \frac{\id \phi }{\id \xi}\right)^2 \right] \, \id\xi +abS_1 \left[\frac{k^r_{\xi=-1}}{a^3} \left( \frac{\id \phi}{\id \xi} \right)^2+ \frac{k^v_{\xi=-1}}{a} \left( \phi \right)^2\right]_{\xi=-1}\\
		&\quad+abS_1 \left[\frac{k^r_{\xi=1}}{a^3} \left( \frac{\id \phi}{\id \xi} \right)^2+ \frac{k^v_{\xi=1}}{a} \left( \phi \right)^2\right]_{\xi=1},

@@

		&S_1 = \int_{-1}^{1} \psi^2 \, \id\eta, \\  
		&S_2 = \int_{-1}^{1} \left( \frac{\id^2 \psi}{\id \eta^2} \psi \right) \, \id\eta, \\  
		&S_3 = \int_{-1}^{1} \left( \frac{\id \psi}{\id \eta} \right)^2 \, \id\eta, \\  
		&S_4 = \int_{-1}^{1} \left( \frac{\id^2 \psi}{\id \eta^2} \right)^2 \, \id\eta.  

@@

By taking \Cref{eq:displace_func} into account, the coefficient \(T_0\) of the kinetic energy in \Cref{eq:kine_energy_mag} for the plate can be expressed as:

@@

		T_0 = \frac{ab}{2}\rho h\iint w^2 \, \id \xi \, \id \eta = \frac{ab}{2}\rho h S_1\int_{-1}^{1} \phi^2 \, \id \xi.

@@

By substituting \Cref{eq:poten_energy_tolx2,eq:kine_energyx} into \Cref{eq:Rayleighx}, relieve \(\delta \phi\) and \(\delta\frac{\id  \phi}{\id \xi}\) in \Cref{eq:Rayleighx} by variation calculus, yielding:

@@

		0 &= \int_{-1}^{1} \bigg[ \frac{D_{11}}{a^4} S_1 \frac{\id^4 \phi}{\id \xi^4} 
		+ \bigg( \frac{2D_{12}}{a^2b^2} S_2 - \frac{4D_{66}}{a^2b^2} S_3 \bigg) \frac{\id^2 \phi}{\id \xi^2} \\
		&\quad + \bigg( \frac{D_{22}}{b^4} S_4 - \omega_x^2 \rho h S_1 \bigg) \phi \bigg] \delta \phi \, \id \xi \\
		&\quad + \frac{2k^v_{\xi=-1}}{a} S_1 \big(\phi \delta \phi\big)_{\xi=-1} 
		+ \frac{2k^v_{\xi=1}}{a} S_1 \big(\phi \delta \phi\big)_{\xi=1} \\
		&\quad + \bigg[ \bigg( \frac{4D_{66}}{a^2b^2} S_3 - \frac{D_{12}}{a^2b^2} S_2 \bigg) \frac{\id \phi}{\id \xi} 
		- \frac{D_{11}}{a^4} S_1 \frac{\id^3 \phi}{\id \xi^3} \bigg] \delta \phi \Big|^{\xi=1}_{\xi=-1} \\
		&\quad + \bigg( \frac{D_{12}}{a^2b^2} S_2 \phi + \frac{D_{11}}{a^4} S_1 \frac{\id^2 \phi}{\id \xi^2} \bigg) 

@@

		&\quad + \frac{2k^r_{\xi=-1}}{a^3} S_1 \bigg(\frac{\id \phi}{\id \xi}\delta \frac{\id \phi}{\id \xi}\bigg)_{\xi=-1} 
		+ \frac{2k^r_{\xi=1}}{a^3} S_1 \bigg(\frac{\id \phi}{\id \xi} \delta\frac{\id \phi}{\id \xi}\bigg)_{\xi=1}.

@@

		\frac{\id^4 \phi}{\id \xi^4}+ 2\alpha^2\left(\frac{D_{12}S_2}{D_{11}S_1}-2\frac{D_{66}S_3}{D_{11}S_1}\right)\frac{\id^2 \phi}{\id \xi^2}+\left(\alpha^4\frac{D_{22}S_4}{D_{11}S_1}-a^4\Omega_x^4\right)\phi=0,

@@

		\mu^4 + 2\alpha^2\left(\frac{D_{12}S_2}{D_{11}S_1}-2\frac{D_{66}S_3}{D_{11}S_1}\right)\mu^2 + \left(\alpha^4\frac{D_{22}S_4}{D_{11}S_1}-a^4\Omega_x^4\right) = 0.

@@

		\alpha_1 &= \alpha \sqrt{\sqrt{\left(\frac{D_{12}S_2}{D_{11}S_1}-2\frac{D_{66}S_3}{D_{11}S_1}\right)^2 - \frac{D_{22}S_4}{D_{11}S_1} + b^4\Omega_x^4} + \frac{D_{12}S_2}{D_{11}S_1} - 2\frac{D_{66}S_3}{D_{11}S_1}},\label{eq:alphax1}\\
		\beta_1 &= \alpha \sqrt{\sqrt{\left(\frac{D_{12}S_2}{D_{11}S_1}-2\frac{D_{66}S_3}{D_{11}S_1}\right)^2 - \frac{D_{22}S_4}{D_{11}S_1} + b^4\Omega_x^4} - \frac{D_{12}S_2}{D_{11}S_1} + 2\frac{D_{66}S_3}{D_{11}S_1}}.\label{eq:alphax2}

@@

		&\left[ \left( \frac{4D_{66}}{a^2b^2} S_3 - \frac{D_{12}}{a^2b^2} S_2 \right) \frac{\id \phi}{\id \xi} 
		- \frac{D_{11}}{a^4} S_1 \frac{\id^3 \phi}{\id \xi^3} \right] \Big|^{\xi=1}_{\xi=-1}\\
		&\quad+ \frac{2k^v_{\xi=-1}}{a} S_1 \left(\phi\right)_{\xi=-1}
		 + \frac{2k^v_{\xi=1}}{a} S_1 \left(\phi\right)_{\xi=1} = 0,

@@

		\left( \frac{D_{12}}{a^2b^2} S_2 \phi + \frac{D_{11}}{a^4} S_1 \frac{\partial^2 \phi}{\partial \xi^2} \right) 

@@

		&+ \frac{2k^r_{\xi=-1}}{a^3} S_1 \left(\frac{\partial \phi}{\partial \xi}\right)_{\xi=-1} \\
		&+ \frac{2k^r_{\xi=1}}{a^3} S_1 \left(\frac{\partial \phi}{\partial \xi}\right)_{\xi=1} = 0.

@@

		&  \frac{\id^3 \phi}{\id \xi^3} - \alpha^2\left( \frac{4D_{66}S_3}{D_{11}S_1}  - \frac{D_{12}S_2}{D_{11}S_1}  \right) \frac{\id \phi}{\id \xi} 

@@

		& \frac{\id^2 \phi}{\id \xi^2} + \frac{\alpha^2 D_{12} S_2}{D_{11} S_1} \phi - \frac{2a k^r_{\xi=-1}}{D_{11}} \frac{\id \phi}{\id \xi} = 0, \quad &\xi = -1, \\

>>>>

% I made some comments about x/L being xi - it's not used much so you can ignore these.
% There are some cases where I added text in [square brackets] and not necessarily in a latex comment
% Check the bib file - two references had no journal - I added these as XXXX
% Section 4 does too much - could you consider splitting this section up a bit? 
% I did add some more subsubsections to try structure section 4 a bit better, but I'm not sure it's optimal yet.
\begin{frontmatter}
\title{The dynamic stiffness matrix based on the extended separation-of-variables type solution for the free vibration of orthotropic rectangular thin plates}
\author[1]{Shiyi Mei}\ead{shiyi.mei1@monash.edu}
\author[1]{Colin Caprani\corref{cor1}}\ead{colin.caprani@monash.edu}
\author[2]{Daniel Cantero}\ead{daniel.cantero@ntnu.no}
\cortext[cor1]{Corresponding author}
\affiliation[1]{organization={Department of Civil Engineering, Monash University},city={Melbourne},state={Victoria},country={Australia}}
\affiliation[2]{organization={Department of Structural Engineering, Norwegian University of Science \& Technology NTNU},city={Trondheim}, country={Norway}}
\begin{abstract}
The dynamic stiffness matrix (DSM) based on the extended separation-of-variables (SOV) type mode solution is developed for the free vibration analysis of an orthotropic rectangular thin plate with general homogeneous boundary conditions.  
The method combines the advantages of the DSM method and the SOV method.
The SOV type solution satisfies the governing differential equation derived from Rayleigh’s principle and is used to formulate the dynamic stiffness matrices.
Owing to the characteristics of the SOV type solution, the fully clamped boundary condition problem associated with the Wittrick–Williams algorithm is resolved. 
The enhanced algorithm is further proposed to solve dynamic stiffness matrices, rather than solving eigenvalue equations.
A numerical technique for mode shape computation is also introduced.
The accuracy of the proposed method is validated through numerical experiments.

\end{abstract}
\end{frontmatter}
\linenumbers
\section{Introduction}
Rectangular plates play an important role in various engineering fields, including civil, mechanical, and aerospace engineering \citep{biancolini2005approximate}. 
The free vibration of plates has been a fundamental research problem for over two centuries. 
The earliest exact solutions for this problem are the Navier \citep{navier1823extrait} and Levy \citep{levy1899equilibre} solutions, which require at least one pair of opposite edges to be simply supported or guided.
To solve problems with other boundary conditions, approximate solutions such as the Rayleigh–Ritz method \cite{leissa1973free} and the Galerkin method \cite{laura1967study} have been widely applied. 
For these approximation methods, beam functions, polynomials, trigonometric functions, and their combinations \cite{li2004vibration} are commonly used as the assumed approximate functions.
The accuracy of these solutions depends on how well the assumed approximate functions represent the displacement of the plate.

@@

Despite being a powerful method for the dynamic analysis of plate assemblies, the finite element method (FEM) requires a sufficient number of elements and is computationally expensive to accurately capture higher-order modes.
Thus, the DSM method was developed as an accurate and efficient analytical approach to alternatively solve complex plate structures \cite{boscolo2011dynamic,fazzolari2013exact}. 
The DSM can be considered as an analytical FEM since the mode functions of the plate are expressed by analytical solutions, where Levy-type solution \cite{ghorbel2015dynamic} or components of infinite Fourier series \cite{banerjee2015dynamic,liu2016free} are applied.
To avoid solving the cumbersome transcendental frequency equation directly, the Wittrick-Williams (W-W) algorithm \cite{wittrick1971general} is applied to the eigenvalue problem.
The W-W algorithm determines the lower and upper bounds of natural frequencies rather than solving the frequency equation directly. 
Thus, the DSM has the potential to be effectively and systematically solved using the W-W algorithm.
However, a critical part in applying the W-W algorithm is to priorly determine all natural frequencies of the fully clamped structure within the interested frequency range.
Strategies such as using a sufficiently fine mesh or including a sufficient number of terms in series expansions \cite{banerjee2015dynamic} can ensure that all fully clamped frequencies are accounted for, thereby maintaining the accuracy of the algorithm. However, these approaches are computationally expensive and complex, posing a significant obstacle to the wider adoption and application of the DSM method based on the W-W algorithm \cite{han2018improved}.
To resolve the fully clamped plate problem, \citet{liu2015exact} suggested that the frequencies can be indirectly obtained from the simply supported plate problem, where the Navier solution serves as the analytical solution. This provides a significant enhancement to the W-W algorithm, increasing the efficiency of applying DSM methods. 
However, the solutions are not explicit and closed-form, but are expressed in an infinite series form, where a sufficient number of truncation terms is required to ensure accuracy.

Inspired by the Navier and Levy solutions, \citet{xing2009new} proposed the separation-of-variables (SOV) method, which provides concise and explicit eigensolutions.
The mode shape function has a separable form, $\phi(x) \psi(y)$, requiring only one $\phi(x)$ and one $\psi(y)$ for each mode order, allowing each eigenvalue equation to be explicitly expressed.
However, this SOV method is not suitable to deal with plates with free boundary conditions.
Therefore, an extended SOV method \cite{xing2018overall, xing2020extended} based on the Rayleigh quotient was proposed to accommodate plates with all four classical boundary conditions, i.e., simply supported, clamped, guided, and free.
Based on the Rayleigh quotient model, alternative iterative and improved SOV methods have been subsequently proposed \cite{xing2020improved}.
Although SOV methods provide concise closed-form analytical solutions, they require solving a specific set of highly nonlinear eigenvalue equations for each type of boundary condition.
However, even when considering only the four classic homogeneous cases, it becomes evident that 55 different boundary condition combinations exist for a rectangular plate, making the process tedious.

In this study, the SOV method is extended to analyze the vibrations of plates with elastically restrained edges.
The extended SOV type solution is then employed to construct the dynamic stiffness matrices, which accommodate all general homogeneous boundary conditions.
By taking advantage of both the SOV and DSM methods, an enhanced W-W algorithm is developed to solve the eigenvalue problem without directly solving the eigenvalue equations.
This enhanced approach resolves the challenge of determining fully clamped frequencies, a well-known limitation in the application of the  W-W algorithm.
In addition, a novel numerical technique has been proposed to compute the mode shape coefficients.

@@

The governing differential equation for the free vibration of a thin orthotropic plate is given by \citep{xing2020improved}:  
%
\begin{equation}\label{eq:governing_EOM}
	D_{11}\frac{\partial^4w}{\partial \xi^4} + 2D_3\alpha^2\frac{\partial^4w}{\partial \xi^2 \partial \eta^2} + D_{22}\alpha^4\frac{\partial^4w}{\partial \eta^4} = \rho h\alpha^4\omega^2w,
\end{equation}
%
where \( \alpha = a / b \) is the aspect ratio; \( \xi = x / a \) and \( \eta = y / b \) are the normalized coordinates,
and the bending stiffness parameters are defined as:
%
\begin{equation}\label{eq:bd_stiff}
	\begin{split}
		&D_{11} = \frac{E_1h^3}{12(1-v_{12}v_{21})}, \quad D_{22} = \frac{E_2h^3}{12(1-v_{12}v_{21})}, \\  
		&D_{66} = \frac{G_{12}h^3}{12}, \quad D_{12} = v_{12}D_{22} = v_{21}D_{11}, \quad D_3 = D_{12} + 2D_{66},
	\end{split}
\end{equation}
%
where \(\rho\) and \(h\) denote the mass density and thickness of the plate, respectively; \(E_1\) and \(E_2\) are the Young’s moduli in the \(x\)- and \(y\)-directions, respectively; \(G_{12}\) is the shear modulus, and \(v_{12}\) and \(v_{21}\) are the Poisson’s ratios.

@@

Assuming the solution of the deflection \( W(x, y; t) = w(x, y) e^{i \omega t} \) for harmonic plate motion, 
where \( \ii = \sqrt{-1} \), \( w(x, y) \) is the mode shape, and \( \omega \) is the radial frequency.  
By substituting \( W(x, y; t) = w(x, y) e^{i \omega t} \) into \Cref{eq:poten_energy,eq:kine_energy} and expressing the system in dimensionless coordinates, we have:
%
\begin{equation}\label{eq:poten_energy_mag}
	\begin{split}
		U_{\text{mag}}^{I} &= \frac{ab}{2} \iint \left[ \frac{D_{11}}{a^4} \left( \frac{\partial^2 w}{\partial \xi^2} \right)^2 + \frac{2 D_{12}}{a^2 b^2} \frac{\partial^2 w}{\partial \xi^2} \frac{\partial^2 w}{\partial \eta^2} + \frac{D_{22}}{b^4} \left( \frac{\partial^2 w}{\partial \eta^2} \right)^2 \right. \\
		&\quad \left. + \frac{4 D_{66}}{a^2 b^2} \left( \frac{\partial^2 w}{\partial \xi \partial \eta} \right)^2 \right] \, \mathrm{d} \xi \, \mathrm{d} \eta,
	\end{split}
\end{equation}
%
and
%
\begin{equation}\label{eq:kine_energy_mag}
	\begin{split}
		T &= \omega^2 \frac{ab}{2} \rho h \iint w^2 \, \mathrm{d} \xi \, \mathrm{d} \eta = \omega^2 T_0
	\end{split},
\end{equation}
%
The separable form of the mode shape function \( w(\xi, \eta) \) is given by:
%
\begin{equation}\label{eq:displace_func}
	w(\xi, \eta) = \phi(\xi) \psi(\eta),
\end{equation}
%
where \( \phi(\xi) \) and \( \psi(\eta) \) can be expressed as:
\begin{subequations}\label{eq:phi_psi_solution}
	\begin{align}
		\phi(\xi) &= A_1 \sin{(\alpha_1 \xi)} + A_2 \cos{(\alpha_1 \xi)} + A_3 \sinh{(\beta_1 \xi)} + A_4 \cosh{(\beta_1 \xi)},\label{eq:phi_solution1}\\
		\psi(\eta) &= B_1 \sin{(\alpha_2 \eta)} + B_2 \cos{(\alpha_2 \eta)} + B_3 \sinh{(\beta_2 \eta)} + B_4 \cosh{(\beta_2 \eta)}. \label{eq:phi_solution2}
	\end{align}
\end{subequations}

Based on \Cref{eq:Rayleigh}, the frequencies $\omega_x$ and $\omega_y$, corresponding to the mode shapes $\phi(\xi)$ and $\psi(\eta)$, respectively, are assumed to be independent of each other.

@@

For given general homogeneous boundary conditions, we can first assume that the mode shape $\psi(\eta)$ corresponding to the $y$-direction is known. 

@@

		&=\frac{ab}{2} \int_{-1}^{1} \left[ \frac{D_{11}}{a^4}I_1 \left( \frac{\id^2\phi }{\id \xi^2} \right)^2 + \frac{2 D_{12}}{a^2 b^2}I_2 \frac{\id^2\phi }{\id \xi^2}\phi  + \frac{D_{22}}{b^4}I_4  \phi^2 \right. \\
		&\quad \left. + \frac{4 D_{66}}{a^2 b^2}I_3 \left( \frac{\id \phi }{\id \xi}\right)^2 \right] \, \id\xi +abI_1 \left[\frac{k^r_{\xi=-1}}{a^3} \left( \frac{\id \phi}{\id \xi} \right)^2+ \frac{k^v_{\xi=-1}}{a} \left( \phi \right)^2\right]_{\xi=-1}\\
		&\quad+abI_1 \left[\frac{k^r_{\xi=1}}{a^3} \left( \frac{\id \phi}{\id \xi} \right)^2+ \frac{k^v_{\xi=1}}{a} \left( \phi \right)^2\right]_{\xi=1},

@@

		&I_1 = \int_{-1}^{1} \psi^2 \, \id\eta, \\  
		&I_2 = \int_{-1}^{1} \left( \frac{\id^2 \psi}{\id \eta^2} \psi \right) \, \id\eta, \\  
		&I_3 = \int_{-1}^{1} \left( \frac{\id \psi}{\id \eta} \right)^2 \, \id\eta, \\  
		&I_4 = \int_{-1}^{1} \left( \frac{\id^2 \psi}{\id \eta^2} \right)^2 \, \id\eta.  

@@

By taking \Cref{eq:displace_func} into account, the coefficient \(T_0\) of the kinetic energy from \Cref{eq:kine_energy_mag} for the plate can be expressed as:

@@

		T_0 = \frac{ab}{2}\rho h\iint w^2 \, \id \xi \, \id \eta = \frac{ab}{2}\rho h I_1\int_{-1}^{1} \phi^2 \, \id \xi.

@@

By substituting \Cref{eq:poten_energy_tolx2,eq:kine_energyx} into \Cref{eq:Rayleighx}, and relieving \(\delta \phi\) and \(\delta\frac{\id  \phi}{\id \xi}\) in \Cref{eq:Rayleighx} by variation calculus, yields:

@@

		0 &= \int_{-1}^{1} \bigg[ \frac{D_{11}}{a^4} I_1 \frac{\id^4 \phi}{\id \xi^4} 
		+ \bigg( \frac{2D_{12}}{a^2b^2} I_2 - \frac{4D_{66}}{a^2b^2} I_3 \bigg) \frac{\id^2 \phi}{\id \xi^2} \\
		&\quad + \bigg( \frac{D_{22}}{b^4} I_4 - \omega_x^2 \rho h I_1 \bigg) \phi \bigg] \delta \phi \, \id \xi \\
		&\quad + \frac{2k^v_{\xi=-1}}{a} I_1 \big(\phi \delta \phi\big)_{\xi=-1} 
		+ \frac{2k^v_{\xi=1}}{a} I_1 \big(\phi \delta \phi\big)_{\xi=1} \\
		&\quad + \bigg[ \bigg( \frac{4D_{66}}{a^2b^2} I_3 - \frac{D_{12}}{a^2b^2} I_2 \bigg) \frac{\id \phi}{\id \xi} 
		- \frac{D_{11}}{a^4} I_1 \frac{\id^3 \phi}{\id \xi^3} \bigg] \delta \phi \Big|^{\xi=1}_{\xi=-1} \\
		&\quad + \bigg( \frac{D_{12}}{a^2b^2} I_2 \phi + \frac{D_{11}}{a^4} I_1 \frac{\id^2 \phi}{\id \xi^2} \bigg) 

@@

		&\quad + \frac{2k^r_{\xi=-1}}{a^3} I_1 \bigg(\frac{\id \phi}{\id \xi}\delta \frac{\id \phi}{\id \xi}\bigg)_{\xi=-1} 
		+ \frac{2k^r_{\xi=1}}{a^3} I_1 \bigg(\frac{\id \phi}{\id \xi} \delta\frac{\id \phi}{\id \xi}\bigg)_{\xi=1}.

@@

		\frac{\id^4 \phi}{\id \xi^4}+ 2\alpha^2\left(\frac{D_{12}I_2}{D_{11}I_1}-2\frac{D_{66}I_3}{D_{11}I_1}\right)\frac{\id^2 \phi}{\id \xi^2}+\left(\alpha^4\frac{D_{22}I_4}{D_{11}I_1}-a^4\Omega_x^4\right)\phi=0,

@@

		\mu^4 + 2\alpha^2\left(\frac{D_{12}I_2}{D_{11}I_1}-2\frac{D_{66}I_3}{D_{11}I_1}\right)\mu^2 + \left(\alpha^4\frac{D_{22}I_4}{D_{11}I_1}-a^4\Omega_x^4\right) = 0.

@@

		\alpha_1 &= \alpha \sqrt{\sqrt{\left(\frac{D_{12}I_2}{D_{11}I_1}-2\frac{D_{66}I_3}{D_{11}I_1}\right)^2 - \frac{D_{22}I_4}{D_{11}I_1} + b^4\Omega_x^4} + \frac{D_{12}I_2}{D_{11}I_1} - 2\frac{D_{66}I_3}{D_{11}I_1}},\label{eq:alphax1}\\
		\beta_1 &= \alpha \sqrt{\sqrt{\left(\frac{D_{12}I_2}{D_{11}I_1}-2\frac{D_{66}I_3}{D_{11}I_1}\right)^2 - \frac{D_{22}I_4}{D_{11}I_1} + b^4\Omega_x^4} - \frac{D_{12}I_2}{D_{11}I_1} + 2\frac{D_{66}I_3}{D_{11}I_1}}.\label{eq:alphax2}

@@

		&\left[ \left( \frac{4D_{66}}{a^2b^2} I_3 - \frac{D_{12}}{a^2b^2} I_2 \right) \frac{\id \phi}{\id \xi} 
		- \frac{D_{11}}{a^4} I_1 \frac{\id^3 \phi}{\id \xi^3} \right] \Big|^{\xi=1}_{\xi=-1}\\
		&\quad+ \frac{2k^v_{\xi=-1}}{a} I_1 \left(\phi\right)_{\xi=-1}
		 + \frac{2k^v_{\xi=1}}{a} I_1 \left(\phi\right)_{\xi=1} = 0,

@@

		\left( \frac{D_{12}}{a^2b^2} I_2 \phi + \frac{D_{11}}{a^4} I_1 \frac{\partial^2 \phi}{\partial \xi^2} \right) 

@@

		&+ \frac{2k^r_{\xi=-1}}{a^3} I_1 \left(\frac{\partial \phi}{\partial \xi}\right)_{\xi=-1} \\
		&+ \frac{2k^r_{\xi=1}}{a^3} I_1 \left(\frac{\partial \phi}{\partial \xi}\right)_{\xi=1} = 0.

@@

		&  \frac{\id^3 \phi}{\id \xi^3} - \alpha^2\left( \frac{4D_{66}I_3}{D_{11}I_1}  - \frac{D_{12}I_2}{D_{11}I_1}  \right) \frac{\id \phi}{\id \xi} 

@@

		& \frac{\id^2 \phi}{\id \xi^2} + \frac{\alpha^2 D_{12} I_2}{D_{11} I_1} \phi - \frac{2a k^r_{\xi=-1}}{D_{11}} \frac{\id \phi}{\id \xi} = 0, \quad &\xi = -1, \\
		& \frac{\id^3 \phi}{\id \xi^3} - \alpha^2\left( \frac{4D_{66}I_3}{D_{11}I_1}  - \frac{D_{12}I_2}{D_{11}I_1}  \right) \frac{\id \phi}{\id \xi} 
